---
title: "Russian Twitter Trolls"
output: github_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Context

After extensive government investigations, it was determined that Russia and Iran tried to influence the U.S. 2016 presidential elections through social media platforms. To work the government in a constructive manner and keep its platform in a positive public light, Twitter made more than ten million foreign troll’s tweets available for research. A team at NBC News reconstructed a dataset of 200,000 Russian troll tweets and made it available on Kaggle. Their research showed these troll accounts were extremely active during key moments around the election. 
This project is attempting to determine which tweets are Russian troll tweets and which are not Russian troll tweets. It will be based on three predictive models, Naïve Bayes, logistic regression, and random forest.  Then we will determine which predictive model is most effective when filtering the Russian troll tweets. This could be one of many possible filtering algorithms to help Twitter in identifying fake accounts of Russian or even Iranian trolls. There are two major reasons for Twitter to identify fake accounts: rebuilding public trust in their platform, and influence in the government’s creation of legislation regulating social media.       


For more background, read the NBC news article publicizing the release: "Twitter deleted 200,000 Russian troll tweets."[NBC Russian Tweets]( https://www.nbcnews.com/tech/social-media/now-available-more-200-000-deleted-russian-troll-tweets-n844731)

Content
This dataset contains two CSV files. tweets.csv includes details on individual tweets from known Russain troll accounts,and noemoticon.csv file that is pre-russain trolls(2009).

To recreate a link to an individual tweet found in the dataset, replace user_key in https://twitter.com/user_key/status/tweet_id with the screen-name from the user_key field and tweet_id with the number in the tweet_id field.

Following the links will lead to a suspended page on Twitter. But some copies of the tweets as they originally appeared, including images, can be found by entering the links on web caches like archive.org and archive.is.

Acknowledgements
If you publish using the data, please credit NBC News and include a link to this page. Send questions to ben.popken@nbcuni.com. 

THIS Project

In this mark down, the russian troll data set and a sentiment data set that was pre 2014 was used for analysis. The Russian troll accounts were from September 2014 until September 2017. So I found tweets that were produced from April to May 2009. Therefore, camparisons of troll and non-troll data could be made.    

```{r}
library(ROCR)
library(caTools)# ROC, AUC
library(e1071) #  Naive Bayes 
library(SnowballC) # stemming
library(gmodels)
library(tidytext)
library(dplyr)
library(ggplot2)
library(wordcloud)
library(tidyr)
library(tm) # text data
library(effects) # regession models
library(glm2)

#nt<-read.csv("C:/Users/John/Documents/R/russian_trolls/training.1600000.processed.noemoticon.csv")
#rt <-read.csv("file:///C:/Users/John/Documents/R/russian_trolls/tweets.csv/tweets.csv")

#set.seed(33)
#rt <- data.frame(sample_n(rt,6000,replace=FALSE))
#nt<-data.frame(sample_n(nt,6000,replace = FALSE))

#save(rt,file = "savedrt.RData")
#save(nt,file= "savednt.RData")


```

Because the CSV files were so large, two Rdata files were created. This helped with a shorter run time and committing to Github.

```{r}

load("savednt.RData")

load("savedrt.RData")

#renameing Features
created_str <-as.Date(rt$created_str)
text<- as.character(rt$text)
colnames(nt)[6]<- as.character(c("text"))
colnames(nt)[3]<- "created_str"

#extracting columns
rtext<-select(rt,"text")
ntext<-select(nt,"text")


#adding a column Russian tweets
rtext$r_nr<-"r"

#adding column to non_russian tweets
ntext$r_nr<-"nr"

```

```{r}

#combining data sets, sample function randomizes order of rows

tot_tweets<- rbind(ntext,rtext,stringAsfactors=FALSE)
tot_tweets <- tot_tweets[sample(nrow(tot_tweets)),]

#change character to factor
tot_tweets$r_nr<-factor(tot_tweets$r_nr, levels=c("r","nr"),ordered=FALSE)

#creating a corpus for the twitter text
text_corpus<- VCorpus(VectorSource(tot_tweets$text))
print(text_corpus)

#cleaning tweets 
text_corpus_clean<-tm_map(text_corpus,content_transformer(tolower))

text_corpus_clean<-tm_map(text_corpus_clean,removeNumbers)

text_corpus_clean<-tm_map(text_corpus_clean,removeWords,stopwords())

text_corpus_clean<-tm_map(text_corpus_clean,removePunctuation)

                                                    text_corpus_clean<-tm_map(text_corpus_clean,stemDocument)
                                                                                                         
text_corpus_clean<-tm_map(text_corpus_clean,stripWhitespace)


#Tokenize the data
text_dtm <-DocumentTermMatrix(text_corpus_clean,control =
                                list(wordLengths=c(0,Inf)))


```

We separate the data into a training set and a test set. Then create the labels for the two sets. 
```{r}
text_dtm_train<- text_dtm[1:10000,]
text_dtm_test<- text_dtm[10001:12000,]


text_train_labels<- tot_tweets[1:10000,]$r_nr
text_test_labels<- tot_tweets[10001:12000,]$r_nr


```


We can now create three word clouds. The first wordcloud shows all of the data together. The second cloud show just the russian troll texts. The third is no Russian trolls at all.
```{r}
#Overall word graph
wordcloud(text_corpus_clean, min.freq = 100,scale=c(2,.5),random.order = FALSE)

#Russian troll graph
rus<-subset(tot_tweets,r_nr=="r")
norus<-subset(tot_tweets,r_nr=="nr")

wordcloud(rus$text, max.words = 40,scale = c(3,.5))

#no russian trolls graph
wordcloud(norus$text, max.words = 40, scale = c(3,.5))
```

```{r}
#number of frequent terms. frenquency filter of words used less than 20 times
tweet_freq_words <- findFreqTerms(text_dtm_train, 20)
 
 str(tweet_freq_words)
 
#create DTM
 
tweet_dtm_freq_train<- text_dtm_train[ , tweet_freq_words]
tweet_dtm_freq_test <- text_dtm_test[ , tweet_freq_words]

#Function for Change to categorical classifier, then apply to the columns
 convert_counts <- function(x) {
 x <- ifelse(x > 0, "Yes", "No")
 }

tweet_train <- apply(tweet_dtm_freq_train, MARGIN = 2,
 convert_counts)
tweet_test <- apply(tweet_dtm_freq_test, MARGIN = 2,
 convert_counts)
  
tweet_classifier<- naiveBayes(tweet_train,text_train_labels)
```

```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
 tweet_test_pred <- predict(tweet_classifier, tweet_test)


 CrossTable(tweet_test_pred, text_test_labels,
 prop.chisq = FALSE, prop.t = FALSE,
 dnn = c('predicted', 'actual'))

 
```
```{r}

#create ROC for Naive Bayes
troc<-predict(tweet_classifier,tweet_test, type = "raw")
predt<- prediction(troc[,"r"],text_test_labels)



#calculate the area
auc<-performance(predt,"auc")


perf_r<- performance(predt, measure ='tpr',x.measure='fpr')
plot(perf_r,colorize=T,main="Naive Bayes")
    
print(auc)


```

```{r echo=TRUE}

library(caret)
library(safeBinaryRegression)
library(glmnet)
library(Matrix)
library(pROC)
 #logistic Regression

sparse_dtm<-removeSparseTerms(text_dtm, 0.995) #terms appear in more than .5% of tweets or 230 

#new Data frame
tweetsSparse<-as.data.frame(as.matrix(sparse_dtm))
colnames(tweetsSparse)<-make.names(colnames(tweetsSparse))
tweetsSparse$r_nr<-tot_tweets$r_nr

#split the data set

trainSparse<- tweetsSparse[1:9000,]
testS<- tweetsSparse[9001:12000,]

#y<-trainSparse[!is.na(trainSparse)]
#x<-model.matrix(r_nr~.,data=trainSparse)[-6510,]
#tweet.logit <-glmnet(x,y, family = "binomial")

tweet.logit<- glm2(r_nr~.,trainSparse, family = "binomial")

tweet.logit.test<-predict(tweet.logit,type = "response", newdata = testS,na.action=na.exclude)


cmatrix_logregr<-table(testS$r_nr, tweet.logit.test>0.5)

cmatrix_logregr

tweet.logit.test1<-predict(tweet.logit, type = "response", newdata = trainSparse)
cmatrix1 <-table(trainSparse$r_nr,tweet.logit.test1>0.5)

cmatrix1

#create ROC for Logistic Regression

troc2<-roc(testS$r_nr~tweet.logit.test)

plot(troc2)

#calculate the area under the ROC
auc2<-performance(troc2,measure = "auc")


print(auc2)


```
```{r}
#Descision Tree
library(rpart)
library(rpart.plot)
tweetcart<- rpart(r_nr~.,data = trainSparse, method = "class")
prp(tweetcart)

predtcart<-predict(tweetcart,newdata=testS,type = "class")
cartable<-table(testS$r_nr,predtcart)


print(cartable)

#Random Forest
library(randomForest)
russianForest<- randomForest(r_nr~.,data=trainSparse,nodesize=25,ntrees=200,na.action=na.roughfix)
predictForest<-predict(russianForest, newdata=testS)

table(testS$r_nr,predictForest)

#random forest ROC
rfroc<-prediction(as.numeric(predictForest),as.numeric(testS$r_nr))
perf_3<- performance(rfroc,measure = 'tpr',x.measure = 'fpr')
plot(perf_3, colorize =T, main= "Random Forest")

```


If any of the three terms rt,trump, or clinton showed themselves in the Russian troll accounts.

Overall Naive Bayes return the most promising results for filtering tweets against a wide range of tweets. 